---
title: "Assignment 1"
output: html_document
---

The data has been loaded to the variable 'data'.

First I open and read the data:
```{r}
setwd('~/coursera/reproducible_research/')
data<-read.csv('activity.csv')
require(ggplot2)
```
#### What is mean total number of steps taken per day?

There are data for `r length(unique(data$date))` days. The total number of steps per day is:
```{r}
steps_hist<-as.data.frame(cbind(unique(data$date),sapply(unique(data$date),function(x) sum(data$steps[data$date==x],na.rm=T))))
names(steps_hist)<-c('Day','Total_Steps')
print(steps_hist)
```
And now, the histogram of the total number of steps is:
```{r}
qplot(x=Total_Steps,data=steps_hist,geom='histogram',binwidth=1000)
```

The mean and the median of the total number of steps per day are `r mean(steps_hist$Total_Steps,na.rm=T)` and `r median(steps_hist$Total_Steps,na.rm=T)` steps per day, respectively.

#### What is the average daily activity pattern?
Plotting the average number of steps taken per interval:
```{r}
qplot(x=interval,y=steps,data=data,stat='summary',fun.y='mean',geom='line')
```

Now, calculating the 5 minutes interval with the largest average of steps:
```{r}
interval_steps<-sapply(unique(data$interval),function(x) mean(data$steps[data$interval==x],na.rm=T))
max_step<-which(interval_steps==max(interval_steps))
```

The interval with the maximum number of steps is `r unique(data$interval)[max_step]` minutes.

#### Imputing missing values
The number of missing data is:
```{r}
sum(is.na(data$steps))
```

The missing values will be filled with the average of the interval:
```{r}
data_filled<-data
missing_vector<-which(is.na(data_filled$steps))
intervals<-unique(data_filled$interval)
data_filled$steps[missing_vector]<-interval_steps[sapply(missing_vector,function(x) which(intervals==data_filled$interval[x]))]
```

And the new histogram is:
```{r}
steps_hist_filled<-as.data.frame(cbind(unique(data_filled$date),sapply(unique(data_filled$date),function(x) sum(data_filled$steps[data_filled$date==x],na.rm=T))))
names(steps_hist_filled)<-c('Day','Total_Steps')
qplot(x=interval,y=steps,data=data_filled,stat='summary',fun.y='mean',geom='line')
```

The histogram doesn't change, but the new mean `r mean(steps_hist_filled$Total_Steps,na.rm=T)` and the median `r median(steps_hist_filled$Total_Steps,na.rm=T)` are slightly different from the original values `r mean(steps_hist$Total_Steps,na.rm=T)` and `r median(steps_hist$Total_Steps,na.rm=T)`. This is because som NA's are replaced by high values and other by small values.

#### Are there differences in activity patterns between weekdays and weekends?
```{r}
data_filled$weekend<-as.factor(weekdays(as.Date(data_filled$date))=="Saturday"|weekdays(as.Date(data_filled$date))=="Sunday")
levels(data_filled$weekend)<-list(Weekday="FALSE",Weekend="TRUE")
ggplot(data_filled,aes(x=interval,y=steps))+stat_summary(geom='line',fun.y='mean')+facet_wrap(~weekend,ncol=1)
```
